---
title: "Question 10 Slides"
author: "Shaun Hutchinson"
format: revealjs
editor: visual
---

## My First Slide

::: incremental
In this presentation I will take you through several slides to highlight some of the many features of Quarto presentations.
:::

## MDS Block One Class Programming Languages

In this slide I have included columns of data for the languages we use in the first block of MDS.

::: columns
::: {.column width="50%"}
Python

-   DSCI 511
-   DSCI 521
:::

::: {.column width="50%"}
R

-   DSCI 521
-   DSCI 523
-   DSCI 551
:::
:::

## R Code

You can include code that only shows the code, without the output using echo:true. As demonstrated with the code for a graph on penguin Bill Length and Body Mass from the palmer penguins dataset

```{r}
#| echo: true
library(tidyverse)
library(palmerpenguins)
options(repr.plot.width = 7, repr.plot.height = 5)
penguins_forcats <- penguins |>
                    mutate(species =fct_reorder(species, body_mass_g)) |>
                    ggplot(mapping = aes(x = bill_length_mm, 
                                      y = body_mass_g,
                                     colour = species)) +
    geom_point(size = 2) +
    xlab("Bill length (mm)") +
    ylab("Body mass (g)") +
    theme_bw() +
    theme(text = element_text(size = 18))
penguins_forcats
```

## R Output

Without using echo:true, the slide will only show the output of the graph as seen below

```{r}

library(tidyverse)
library(palmerpenguins)
options(repr.plot.width = 7, repr.plot.height = 5)
penguins_forcats <- penguins |>
                    mutate(species =fct_reorder(species, body_mass_g)) |>
                    ggplot(mapping = aes(x = bill_length_mm, 
                                      y = body_mass_g,
                                     colour = species)) +
    geom_point(size = 2) +
    xlab("Bill length (mm)") +
    ylab("Body mass (g)") +
    theme_bw() +
    theme(text = element_text(size = 18))
penguins_forcats
```

## Python

You can also include python code chunks in the presentation

``` python
courses = list("DSCI 511", "DSCI 521", "DSCI 523", "DSCI 551")
for class in courses:
  print(class)
```
